An Extension of LTL with Rules\\ and its Application to Runtime Verification

### 2019-02-07 implementation.tex

\subsubsection{Example Properties}

Figure \ref{fig:properties} shows three properties in the 
input format of the tool, which are not expressible in the original first-order logic of \dejavu{} presented in \cite{HPU}. 
%
The ASCII version of the logic here uses 
\idsl{@} for $\ominus$,
\idsl{|} for $\vee$,
\idsl{&} for $\wedge$, and
\idsl{!} for $\neg$.
%
The first property \idsl{telemetry1} is a variant of
formula \ref{eq:wolper-first-order}, illustrating the use of a 
rule to express a first-order version of Wolper's example \cite{Wolper}, that all the states with even indexes of a sequence satisfy a property.
In this case we consider a radio on board a spacecraft, which communicates over different channels (quantified over in the formula), which can be turned on and off with a \idsl{toggle(x)} - they are initially off.
Telemetry can only be sent to ground over a channel \idsl{x} with the \idsl{telem(x)} event when radio channel \idsl{x} is toggled on.

\begin{center}
\begin{figure}
\begin{lstlisting}[language=dsl,frame=single,linewidth=0.95\textwidth,backgroundcolor=\color{white},linewidth=\columnwidth,breaklines=true,basicstyle=\small]
prop telemetry1: 
  Forall x . closed(x) -> !telem(x) where closed(x) := toggle(x) <-> @!closed(x)

prop spawning :
  Forall x . Forall y . Forall d . report(y,x,d) -> spawned(x,y) where
    spawned(x,y) := @ spawned(x,y) | spawn(x,y) | 
                    Exists z . (@spawned(x,z) & spawn(z,y))
\end{lstlisting}
\caption{Three properties stated in \dejavu's logic}
\label{fig:properties}
\end{figure}
\end{center}

@@

\subsubsection{Monitor Synthesis}

@@

\subsubsection{Evaluation}

We evaluated the three properties in Figure 
\ref{fig:properties} on a collection of traces. Table \ref{tab:evaluation} shows the  
analysis time (excluding time to compile the generated 
monitor) for different traces (format is `trace length : seconds'). The telemetry traces will repeatedly open hundreds of channels and send telemetry over them. 
%
The spawning traces consist of 50\% spawning events and 50\% reporting events. The spawning property  requires larger processing time compared to the telemetry properties since more data (the transitive closure) has to be computed and stored.

>>>>

\vspace{1ex}\noindent {\bf Example Properties.}
Figure \ref{fig:properties} shows three properties in the 
input format of the tool, which are not expressible in the original first-order logic of \dejavu{} presented in \cite{HPU}. The properties are related to the examples in Section~\ref{sec:syntax-semantics}, which
are not expressible in (P)FLTL.
%
The ASCII version of the logic here uses 
\idsl{@} for $\ominus$,
\idsl{|} for $\vee$,
\idsl{&} for $\wedge$, and
\idsl{!} for $\neg$.
%
The first property \idsl{telemetry1} is a variant of
formula \ref{eq:wolper-first-order}, illustrating the use of a 
rule to express a first-order version of Wolper's example \cite{Wolper}, that all the states with even indexes of a sequence satisfy a property.
In this case we consider a radio on board a spacecraft, which communicates over different channels (quantified over in the formula), which can be turned on and off with a \idsl{toggle(x)} - they are initially off.
Telemetry can only be sent to ground over a channel \idsl{x} with the \idsl{telem(x)} event when radio channel \idsl{x} is toggled on.

%%%%

@@

\begin{figure}
\begin{center}
\begin{lstlisting}[language=dsl,frame=single,linewidth=0.95\textwidth,backgroundcolor=\color{white},linewidth=\columnwidth,breaklines=true,basicstyle=\small]
prop telemetry1: 
  Forall x . closed(x) -> !telem(x) where closed(x) := toggle(x) <-> @!closed(x)

prop spawning :
  Forall x . Forall y . Forall d . report(y,x,d) -> spawned(x,y) where
    spawned(x,y) := @ spawned(x,y) | spawn(x,y) | 
                    Exists z . (@spawned(x,z) & spawn(z,y))
\end{lstlisting}
\caption{Three properties stated in \dejavu's logic}
\label{fig:properties}
\end{center}
\end{figure}

\iffalse
\subsubsection{Monitor Synthesis}

@@

\fi

\vspace{1ex}\noindent {\bf Evaluation.}
We evaluated the three properties in Figure 
\ref{fig:properties} on a collection of traces. Table \ref{tab:evaluation} shows the  
analysis time (excluding time to compile the generated 
monitor) for different traces (format is `trace length : seconds'). The telemetry traces will repeatedly open hundreds of channels and send telemetry over them. 
%
The spawning traces consist of 50\% spawning events and 50\% reporting events. The spawning property  requires larger processing time compared to the telemetry properties since more data (the transitive closure) has to be computed and stored.
